Verifying Demonstrations

### 2018-10-31 paper/privacy-properties.tex
split privacy requirement p2 in two

We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} \emph{Anonymity}: participants' real (long-term) 
  identities must be unlinkable to their proofs.
\item\label{ProtestUnlink} \emph{Unlinkability}: protesters' proofs must be 
  unlinkable between protests and witnesses' proofs must be unlinkable between 
  protesters.
\end{requirements}

>>>>

We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: participants' real (long-term) 
  identities must be unlinkable to their proofs.
\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters' proofs must be 
  unlinkable between protests 
\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses' proofs must be unlinkable between 
  protesters.
\end{requirements}
